Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-19 manuscript/main.tex
beta smoothness

% \definecolor{myblue}{RGB}{0, 0, 0}
% \newcommand{\blue}[1]{{\color{myblue}#1}}
\startlocaldefs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Uncomment next line to change            %%
%% the type of equation numbering           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\numberwithin{equation}{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Axiom, Claim, Corollary, Hypothesis, %%
%% Lemma, Theorem, Proposition              %%
%% use \theoremstyle{plain}                 %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{axiom}{Axiom}
\newtheorem{claim}[axiom]{Claim}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Assumption, Definition, Example,     %%
%% Notation, Property, Remark, Fact         %%
%% use \theoremstyle{definition}            %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{example}{Example}
\newtheorem*{fact}{Fact}
\newtheorem{remark}{Remark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please put your definitions here:        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand{\jongmin}[1]{
	{ \color{teal} \textit{(JM: #1)}}
}

@@

	\section{Background on partial least squares and its extension to hybrid predictors}  
	\jongmin{I replaced the formal presentation of the naive algorithm with an   the scalar version and a brief outline of the pointwise hybrid  extension strategy. The main reason for this revision is that the hybrid inner product is introduced specifically to address the extension challenge, so it is more natural to present it after listing the challenges. Previously, the naive algorithm section relied on the hybrid inner product for normalization.}
	For intuition, let us return to the high-dimensional Euclidean predictor setting $
	Y_i =  \boldsymbol{\beta}^\top \mathbf{Z}_i + \epsilon_i$.
	A common way to address ill-posedness and correlation is to approximate the high-dimensional vector $\mathbf{Z}_i$ using a low-dimensional vector $
	\bigr(
	\widehat{\rho}_1^{[1]}, \ldots,   \widehat{\rho}_1^{[L]}  
	\bigr)^\top \in \mathbb{R}^L.
	$ To retain the regression relationship, the $l$-th PLS direction $\hat{\boldsymbol{\xi}}_l$ solves:
	\begin{equation*}
		\max_{ \boldsymbol{ \alpha } } 
		\widehat{\operatorname{Cov}}^2
		\bigl(
		\{
		\langle 
		\boldsymbol{\alpha}, \mathbf{Z}_i
		\rangle
		, Y_i
		\}_{i=1}^n
		\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1,~\boldsymbol{\alpha}^\top  \widehat{\operatorname{Cov}}^2
		\bigl(
		\{
		\mathbf{Z}_i
		\}_{i=1}^n
		\bigr) \hat{\boldsymbol{\xi}}_j = 0, \quad j = 1, \ldots, l-1,
	\end{equation*}
	where the two $\widehat{\operatorname{Cov}}^2$ denote sample cross-covariance and sample covariance, respectively. A standard algorithm for solving this problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{alg:scalar_pls}.
	\begin{algorithm} 
		\caption{Scalar partial least squares regression}\label{alg:scalar_pls}
		\begin{algorithmic}[1]
			\State Standardize each $\mathbf{Z}_1, \ldots, \mathbf{Z}_n$ so that each feature have mean zero and variance one. Standardize $Y_1, \ldots, Y_n$.
			\For{$l = 1, 2, \ldots, L$}
			\\
			\textbf{PLS direction and score estimation:}
			\State $\widehat{\boldsymbol{\xi}}^{[l]} \leftarrow
			\arg \max_{  \boldsymbol{\alpha}   } 
			\widehat{\operatorname{Cov}}^2
			\bigl(
			\{
			\langle 
			\boldsymbol{\alpha}, \mathbf{Z}^{[l]}_i
			\rangle
			, Y^{[l]}_i
			\}_{i=1}^n
			\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1
			$
			\Comment{PLS direction}\label{alg:step:scalar_pls_direction}
			\State 
			$
			\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\boldsymbol{\xi}}^{[l]},   \mathbf{Z}^{[l]}_i \rangle, 
			~i=1,  \ldots, n
			$ \Comment{PLS score}
			\\
			\textbf{Residualization:}
			\State $\nu^{[l]} 
			\leftarrow
			\frac{
				\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{i}^{[l]}}{
				\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}
			}$ \Comment{Least squares estimate} 
			%
			\State $ Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \nu^{[l]}\widehat{\rho}_i^{[l]}~i=1,  \ldots, n$
			%
			\State $ \widehat{\boldsymbol{\delta}}^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\mathbf{Z}_i^{[l]} $ \Comment{Least squares estimate} 
			\label{alg:step:scalar_pls_residualization}
			\State $\mathbf{Z}_i^{[l+1]}  \leftarrow \mathbf{Z}_i^{[l]} -   \widehat{\rho}_{i}^{[l]}  \widehat{\boldsymbol{\delta}}^{[l]} $
			\EndFor
			\textbf{Regression coefficient estimation:}
			\State
			$\widehat{\boldsymbol{\iota}}^{[1]} \leftarrow \widehat{\boldsymbol{\xi}}^{[1]}$
			\For{$l =  2, \ldots, L$}
			\State $\widehat{\boldsymbol{\iota}}^{[l]} \leftarrow \widehat{ \boldsymbol{\xi} }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}^{[u]}, \widehat{\boldsymbol{\xi}}^{[l]} \rangle 
			\widehat{\boldsymbol{\iota}}^{[u]}$  
			\EndFor
			$	\widehat{\boldsymbol{\beta}} \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{\boldsymbol{\iota}}^{[l]}$ \Comment{regression coefficient estimate}
			\State \textbf{Output:} the  regression coefficient estimate
		\end{algorithmic}
	\end{algorithm}

@@

	\section{Proposed PLS Algorithm} \label{section:main:our_algorithm}
	Our new framework builds on the fact that all computations in Algorithm \ref{alg:scalar_pls} are arithmetic operations in an inner product space. We therefore formally define the Hilbert space of hybrid random predictors along with its corresponding complete inner product, and leverage them to extend Algorithm \ref{alg:scalar_pls}.
	\jongmin{I split the definition into three parts, adding completeness, separability, and the sigma-field.}
	\begin{definition}[Hybrid space]\label{def:hilbert_space}
		Let $\mathbb{H}$ be a product space defined as the Cartesian product of $K$ copies of the space of square-integrable functions on $[0,1]$ and the $p$-dimensional Euclidean space:
		$$
		\mathbb{H} := (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p.
		$$
		An element $h \in \mathbb{H}$ is an ordered tuple $h = (f_1, \dots, f_K, \mathbf{u})$, where $f_k \in \mathbb{L}^2[0,1]$ for $k=1, \dots, K$ and $\mathbf{u} \in \mathbb{R}^p$. This space is equipped with element-wise vector addition and scalar multiplication.
		We define an inner product on $\mathbb{H}$ for any two elements $h_1 = (f_1, \dots, f_K, \mathbf{u})$ and $h_2 = (g_1, \dots, g_K, \mathbf{v})$ as:
		\begin{equation}\label{eq: hybrid inner product}
			\langle h_1, h_2 \rangle_{\mathbb{H}} := \sum_{k=1}^K \int_0^1 f_k(t) g_k(t) \, dt + \omega \mathbf{u}^\top \mathbf{v},
		\end{equation}
		where $\omega$ is a positive constant ($\omega > 0$).
		The inner product induces a norm $\Vert \cdot \Vert_{\mathbb{H}}$ on the space, defined as $\Vert h \Vert_{\mathbb{H}} := \langle h, h \rangle_{\mathbb{H}}^{1/2}$, and a corresponding metric $d(h_1, h_2) = \Vert h_1 - h_2 \Vert_{\mathbb{H}}$.
	\end{definition}
	In \eqref{eq: hybrid inner product}, 
	$\omega$ is a positive weight that needs to be pre-specified or estimated. It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
	Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. 
	\begin{lemma}[Hybrid Hilbert space]\label{lemma:hybrid_hilbert_space}
		The hybrid space $\mathbb{H}$ is a separable Hilbert space.
	\end{lemma} 
	Proof of Lemma \ref{lemma:hybrid_hilbert_space} is provided in Appendix \ref{section:proof:lemma:hybrid_hilbert_space}.

@@

	\medskip
	\noindent
	\textit{Proposed regularized estimation procedure.}~ \label{sec: Regularization of PLS Components}
	Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions. To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative 
	\begin{equation}\label{def:roughness_penalty}
		\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
		.
	\end{equation}

@@

	\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
	The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
	\begin{equation}\label{def:plsscore}
		\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathbb{H}},
	\end{equation}
	using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
	Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
	To obtain the $(l+1)$-th  iteration's responses and hybrid predictors, we regress the $(l)$-th iteration's responses and hybrid predictors on  
	these PLS scores by least squares and then residualize. 
	Specifically,
	the $(l+1)$-th predictor is computed as a residual of hybrid-on-scalar linear regression model:
	\begin{equation*}
		\widetilde{W}_i^{[l]}  =
		\widehat{\rho}_i^{[l]}
		\hat{\delta}^{[l]} + \epsilon_i,
	\end{equation*}
	where $\hat{\delta}^{[l]} \in \widetilde{\mathbb{H}}$ is the regression coefficient.
	In the same spirit as the PLS component direction estimation step,
	rather than treating the hybrid object as a long vector of concatenated function evaluations at time points and scalar vectors,
	we employ a basis expansion approach to fit the entire hybrid object in one step.
	Therefore, our method is computationally efficient, and applicable for dense or irregular functional data.
	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
	least squares criterion: \jongmin{I removed the penalization because it makes proving the orthonormality of the PLS components in Proposition \ref{proposition: modified orthnormality of PLS components} impossible.}
	\begin{equation}\label{def:argmin_pensse}
		\hat{\delta}^{[l]} := \arg \min_{\delta \in \widetilde{\mathbb{H}}} \sum_{i=1}^n 
		\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathbb{H}}^2.
	\end{equation}
	On the other hand, the $(l+1)$-th response   is computed as a residual of a scalar-on-scalar linear regression model:
	\begin{equation*}
		Y_i^{[l]}  =
		\hat{\nu}^{[l]}   	\widehat{\rho}_i^{[l]} + \epsilon_i.
	\end{equation*}
	The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
		Let us denote
		$
		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
		%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
		$
		The $(l+1)$-th iteration's  predictors and responses are computed as
		\begin{equation*}
			\widetilde{W}_i^{[l+1]} 
			:= 	\widetilde{W}_i^{[l]}  - 
			\widehat{\rho}_i^{[l]}
			\hat{\delta}^{[l]},~\text{where}~
			\delta^{[l]}
			:= 
			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
			\sum_{i=1}^n 
			\widehat{\rho}_i^{[l]}
			\widetilde{W}_i^{[l]},
			%%%%%%%%%%% 
			,
		\end{equation*} 	
		and
		\begin{equation}\label{algorithm_step:residualization_predictor}
			Y_i^{[l+1]} = Y_i^{[l]} - 
			\hat{\nu}^{[l]} 
			\widehat{\rho}_i^{[l]},~\text{where}~\hat{\nu}^{[l]} :=  
			\frac{
				\mathbf{y}^{[l] \top }  \hat{\boldsymbol{\rho}}^{[l]}
			}{
				\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2
			}.
		\end{equation}
	\end{lemma}
	Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
	\jongmin{proof needs to be revised}
	Since $\widetilde{W}_i^{[l]}$ and $Y_i^{[l]}$ are assumed to have a sample mean of zero, their respective residuals, $\widetilde{W}_i^{[l+1]}$ and $Y_i^{[l+1]}$, also maintain a zero sample mean.

@@

Next,  \eqref{algorithm_step:residualization_predictor} leads to the following model:
	\begin{equation*}
		Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{\rho}_i^{[l]} + \epsilon_i.
	\end{equation*}
	This model lets us to express $Y_i$ as:
	\begin{equation*}
		Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \langle W_i^{[l]}, \widehat{\xi}^{[l]} \rangle_\mathbb{H} +\epsilon_i 
		= 
		\bigl \langle W_i, \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
		\bigr \rangle_\mathbb{H}+\epsilon_i,
	\end{equation*}
	which, given the uniqueness of $ \beta $, leads to
	\begin{equation*}
		\widehat{ \beta} = \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}.
	\end{equation*}
	Here, the number of PLS components $L$ to be estimated can be chosen by cross-validation.

>>>>

% \definecolor{myblue}{RGB}{0, 0, 0}
% \newcommand{\blue}[1]{{\color{myblue}#1}}
\startlocaldefs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Uncomment next line to change            %%
%% the type of equation numbering           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\numberwithin{equation}{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Axiom, Claim, Corollary, Hypothesis, %%
%% Lemma, Theorem, Proposition              %%
%% use \theoremstyle{plain}                 %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{axiom}{Axiom}
\newtheorem{claim}[axiom]{Claim}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Assumption, Definition, Example,     %%
%% Notation, Property, Remark, Fact         %%
%% use \theoremstyle{definition}            %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{example}{Example}
\newtheorem*{fact}{Fact}
\newtheorem{remark}{Remark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please put your definitions here:        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand{\jongmin}[1]{
	{ \color{teal} \textit{(JM:) #1}}
}

@@

	\section{Background on partial least squares and its extension to hybrid predictors}  
	\jongmin{comment: I replaced the formal presentation of the naive algorithm with an   the scalar version and a brief outline of the pointwise hybrid  extension strategy. The main reason for this revision is that the hybrid inner product is introduced specifically to address the extension challenge, so it is more natural to present it after listing the challenges. Previously, the naive algorithm section relied on the hybrid inner product for normalization.}
	For intuition, let us return to the high-dimensional Euclidean predictor setting $
	Y_i =  \boldsymbol{\beta}^\top \mathbf{Z}_i + \epsilon_i$.
	A common way to address ill-posedness and correlation is to approximate the high-dimensional vector $\mathbf{Z}_i$ using a low-dimensional vector $
	\bigr(
	\widehat{\rho}_1^{[1]}, \ldots,   \widehat{\rho}_1^{[L]}  
	\bigr)^\top \in \mathbb{R}^L.
	$ To retain the regression relationship, the $l$-th PLS direction $\hat{\boldsymbol{\xi}}_l$ solves:
		\max_{ \boldsymbol{ \alpha } } 
		\widehat{\operatorname{Cov}}^2
		\{
		\boldsymbol{\alpha}, \mathbf{Z}_i
		\rangle
		, Y_i
		\}_{i=1}^n
		\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1,~\boldsymbol{\alpha}^\top  \widehat{\operatorname{Cov}}^2
		\{
		\mathbf{Z}_i
		\}_{i=1}^n
		\bigr) \hat{\boldsymbol{\xi}}_j = 0, \quad j = 1, \ldots, l-1,
	where the two $\widehat{\operatorname{Cov}}^2$ denote sample cross-covariance and sample covariance, respectively. A standard algorithm for solving this problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{alg:scalar_pls}.
	\begin{algorithm} 
		\caption{Scalar partial least squares regression}\label{alg:scalar_pls}
		\begin{algorithmic}[1]
			\State Standardize each $\mathbf{Z}_1, \ldots, \mathbf{Z}_n$ so that each feature have mean zero and variance one. Standardize $Y_1, \ldots, Y_n$.
			\For{$l = 1, 2, \ldots, L$}
			\textbf{PLS direction and score estimation:}
			\State $\widehat{\boldsymbol{\xi}}^{[l]} \leftarrow
			\arg \max_{  \boldsymbol{\alpha}   } 
			\widehat{\operatorname{Cov}}^2
			\{
			\boldsymbol{\alpha}, \mathbf{Z}^{[l]}_i
			\rangle
			, Y^{[l]}_i
			\}_{i=1}^n
			\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1
			\Comment{PLS direction}\label{alg:step:scalar_pls_direction}
			\State 
			\widehat{\rho}_i^{[l]} \leftarrow \langle \hat{\boldsymbol{\xi}}^{[l]},   \mathbf{Z}^{[l]}_i \rangle, 
			~i=1,  \ldots, n
			$ \Comment{PLS score}
			\textbf{Residualization:}
			\State $\nu^{[l]} 
			\leftarrow
				\sum_{i=1}^n Y_i^{[l]} \widehat{\rho}_{i}^{[l]}}{
				\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}
			}$ \Comment{Least squares estimate} 
			\State $ Y_i^{[l+1]} \leftarrow Y_i^{[l]} - \nu^{[l]}\widehat{\rho}_i^{[l]}~i=1,  \ldots, n$
			\State $ \widehat{\boldsymbol{\delta}}^{[l]}  \leftarrow \frac{1}{\sum_{i=1}^n \widehat{\rho}_{i}^{[l]2}}\sum_{i=1}^n  \widehat{\rho}_{i}^{[l]}\mathbf{Z}_i^{[l]} $ \Comment{Least squares estimate} 
			\label{alg:step:scalar_pls_residualization}
			\State $\mathbf{Z}_i^{[l+1]}  \leftarrow \mathbf{Z}_i^{[l]} -   \widehat{\rho}_{i}^{[l]}  \widehat{\boldsymbol{\delta}}^{[l]} $
			\EndFor
			\textbf{Regression coefficient estimation:}
			\State
			$\widehat{\boldsymbol{\iota}}^{[1]} \leftarrow \widehat{\boldsymbol{\xi}}^{[1]}$
			\For{$l =  2, \ldots, L$}
			\State $\widehat{\boldsymbol{\iota}}^{[l]} \leftarrow \widehat{ \boldsymbol{\xi} }^{[l]} - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}^{[u]}, \widehat{\boldsymbol{\xi}}^{[l]} \rangle 
			\widehat{\boldsymbol{\iota}}^{[u]}$  
			\EndFor
			$	\widehat{\boldsymbol{\beta}} \leftarrow \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{\boldsymbol{\iota}}^{[l]}$ \Comment{regression coefficient estimate}
			\State \textbf{Output:} the  regression coefficient estimate
		\end{algorithmic}
	\end{algorithm}

@@

	\section{Proposed PLS Algorithm} \label{section:main:our_algorithm}
	Our new framework builds on the fact that all computations in Algorithm \ref{alg:scalar_pls} are arithmetic operations in an inner product space. We therefore formally define the Hilbert space of hybrid random predictors along with its corresponding complete inner product, and leverage them to extend Algorithm \ref{alg:scalar_pls}.
	\jongmin{comment: I split the definition into three parts, adding completeness, separability, and the sigma-field.}
	\begin{definition}[Hybrid space]\label{def:hilbert_space}
		Let $\mathbb{H}$ be a product space defined as the Cartesian product of $K$ copies of the space of square-integrable functions on $[0,1]$ and the $p$-dimensional Euclidean space:
		$$
		\mathbb{H} := (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p.
		$$
		An element $h \in \mathbb{H}$ is an ordered tuple $h = (f_1, \dots, f_K, \mathbf{u})$, where $f_k \in \mathbb{L}^2[0,1]$ for $k=1, \dots, K$ and $\mathbf{u} \in \mathbb{R}^p$. This space is equipped with element-wise vector addition and scalar multiplication.
		We define an inner product on $\mathbb{H}$ for any two elements $h_1 = (f_1, \dots, f_K, \mathbf{u})$ and $h_2 = (g_1, \dots, g_K, \mathbf{v})$ as:
		\begin{equation}\label{eq: hybrid inner product}
			\langle h_1, h_2 \rangle_{\mathbb{H}} := \sum_{k=1}^K \int_0^1 f_k(t) g_k(t) \, dt + \omega \mathbf{u}^\top \mathbf{v},
		\end{equation}
		where $\omega$ is a positive constant ($\omega > 0$).
		The inner product induces a norm $\Vert \cdot \Vert_{\mathbb{H}}$ on the space, defined as $\Vert h \Vert_{\mathbb{H}} := \langle h, h \rangle_{\mathbb{H}}^{1/2}$, and a corresponding metric $d(h_1, h_2) = \Vert h_1 - h_2 \Vert_{\mathbb{H}}$.
	\end{definition}
	In \eqref{eq: hybrid inner product}, 
	$\omega$ is a positive weight that needs to be pre-specified or estimated. It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}).
	Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. 
	\begin{lemma}[Hybrid Hilbert space]\label{lemma:hybrid_hilbert_space}
		The hybrid space $\mathbb{H}$ is a separable Hilbert space.
	\end{lemma} 
	Proof of Lemma \ref{lemma:hybrid_hilbert_space} is provided in Appendix \ref{section:proof:lemma:hybrid_hilbert_space}.

@@

	\medskip
	\noindent
	\textit{Proposed regularized estimation procedure.}~ \label{sec: Regularization of PLS Components}
Although Proposition \ref{proposition:eigen_noregul} offers an efficient way to estimate the PLS component direction $\hat{\xi}$, its functional components, $\hat{\xi}_1, \ldots, \hat{\xi}_K$, may not be smooth. \jongmin{added: Since  the final regression coefficient $\hat{\beta}$ is constructed as a linear combination of these directions (Section \ref{section:sub:regression_coeff}),
this can lead to a non-smooth $\hat{\beta}$} which complicates interpretation and can lead to overfitting and unstable predictions. 
	To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative 
	\begin{equation}\label{def:roughness_penalty}
		\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
		.
	\end{equation}

@@

	\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
	The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
	\begin{equation}\label{def:plsscore}
		\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathbb{H}},
	using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
	Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
	To obtain the $(l+1)$-th  iteration's responses and hybrid predictors, we regress the $(l)$-th iteration's responses and hybrid predictors on  
	these PLS scores by least squares and then residualize. 
	Specifically,
	the $(l+1)$-th predictor is computed as a residual of hybrid-on-scalar linear regression model:
		\widetilde{W}_i^{[l]}  =
		\hat{\delta}^{[l]} + \epsilon_i,
	where $\hat{\delta}^{[l]} \in \widetilde{\mathbb{H}}$ is the regression coefficient.
	In the same spirit as the PLS component direction estimation step,
	rather than treating the hybrid object as a long vector of concatenated function evaluations at time points and scalar vectors,
	we employ a basis expansion approach to fit the entire hybrid object in one step.
	Therefore, our method is computationally efficient, and applicable for dense or irregular functional data.
	Consequently, $\delta^{[l]}$ is obtained by minimizing a  
	least squares criterion: \jongmin{comment: I removed the penalization because it makes proving the orthonormality of the PLS components in Proposition \ref{proposition: modified orthnormality of PLS components} impossible. Smoothness of $\beta$ seems to soley rely on the smoothness of $\xi$. See Section \ref{section:sub:regression_coeff}.}
	\begin{equation}\label{def:argmin_pensse}
		\hat{\delta}^{[l]} := \arg \min_{\delta \in \widetilde{\mathbb{H}}} \sum_{i=1}^n 
		\| \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta\|_{\mathbb{H}}^2.
	On the other hand, the $(l+1)$-th response   is computed as a residual of a scalar-on-scalar linear regression model:
		Y_i^{[l]}  =
		\hat{\nu}^{[l]}   	\widehat{\rho}_i^{[l]} + \epsilon_i.
	The following proposition demonstrates that this residualization step can be performed simply, analogous to scalar PLS.
	\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}\jongmin{Previously stated as "we can show".}
		Let us denote
		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
		%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
		The $(l+1)$-th iteration's  predictors and responses are computed as
			\widetilde{W}_i^{[l+1]} 
			:= 	\widetilde{W}_i^{[l]}  - 
			\hat{\delta}^{[l]},~\text{where}~
			\widetilde{W}_i^{[l]},
			%%%%%%%%%%% 
		\begin{equation}\label{algorithm_step:residualization_predictor}
			Y_i^{[l+1]} = Y_i^{[l]} - 
			\hat{\nu}^{[l]} 
			\widehat{\rho}_i^{[l]},~\text{where}~\hat{\nu}^{[l]} :=  
				\| \hat{\boldsymbol{\rho}}^{[l]} \|_2^2
			}.
	\end{lemma}
	Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
	\jongmin{proof needs to be revised}
	Since $\widetilde{W}_i^{[l]}$ and $Y_i^{[l]}$ are assumed to have a sample mean of zero, their respective residuals, $\widetilde{W}_i^{[l+1]}$ and $Y_i^{[l+1]}$, also maintain a zero sample mean.

@@

Next,  \eqref{algorithm_step:residualization_predictor} leads to the following model:
	\begin{equation*}
		Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{\rho}_i^{[l]} + \epsilon_i.
	\end{equation*}
	This model lets us to express $Y_i$ as:
	\begin{equation*}
		Y_i = \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \langle W_i^{[l]}, \widehat{\xi}^{[l]} \rangle_\mathbb{H} +\epsilon_i 
		= 
		\bigl \langle W_i, \sum \limits_{l=1}^L \widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
		\bigr \rangle_\mathbb{H}+\epsilon_i,
	\end{equation*}
	which, given the uniqueness of $ \beta $, leads to
	\begin{equation*}
		\widehat{ \beta} = \sum \limits_{l=1}^L\widehat{\nu}^{[l]} \widehat{ \iota }^{[l]}
		=\jongmin{added:}
	 \sum_{l=1}^L \left( \widehat{\nu}^{[l]} - \sum_{k=l+1}^L \widehat{\nu}^{[k]} \langle \widehat{\delta}^{[l]}, \widehat{\xi}^{[k]} \rangle_{\mathbb{H}} \right) \widehat{\xi}^{[l]}.
	\end{equation*}
	\jongmin{added: Note that if $L$ is too large, $\widehat{ \beta}$ can be wiggly even if $\widehat{\xi}^{[l]}$'s are smooth.}
	Thus the number of PLS components $L$ to be estimated can be chosen by cross-validation.
